Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2016-12-20 paper/structureScene.tex
edit supervised results
edit GL bio

\begin{table}
\begin{center}
\caption{
\label{table:dcase2013}
Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.
}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
\emph{early}, linear  & $54\pm19$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
\emph{early}, RBF     & $47\pm16$  & $61\pm\phantom{0}9$  & $63\pm\phantom{0}6$   \\
\emph{late}, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
\emph{late}, RBF     & $68\pm14$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\end{center}
\end{table}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lafay}}]{Gr\'egoire Lafay} was born in Paris, France, in 1990. He received in 2011 the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, France, and the B.S. degree in Musicology from the Sorbonne University, Paris, France. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the Universit\'{e} Pierre and Marie Curie and the Ircam in Paris, France, in 2013. Since 2013, he is a Ph.D. student at IRCCyN, a French laboratory dedicated to cybernetics. His research interests include acoustic scene similarity and classification as well as acoustic scene perception. 
\end{IEEEbiography}

>>>>

\begin{table}
\begin{center}
\caption{
\label{table:dcase2013}
Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.
}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
\emph{early}, linear  & $54\pm19$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
\emph{early}, RBF     & $47\pm16$  & $61\pm\phantom{0}9$  & $63\pm\phantom{0}6$   \\
\emph{late}, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
\emph{late}, RBF     & $68\pm14$ & $73\pm\phantom{0}6$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\end{center}
\end{table}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{gfx/lafay}}]{Gr\'egoire Lafay} was born in 1990. He received the B.S. degree in Acoustic from the University Pierre and Marie Curie (UPMC), Paris, France, and the B.S. degree in Musicology from the Sorbonne University, Paris, France, in 2011. He received his M.S. degree in acoustics, signal processing, and musical informatics (ATIAM) from the UPMC and the Ircam in Paris, France, in 2013. Since 2013, he is a Ph.D. student at IRCCyN, Nantes, France. His research interests include acoustic scene similarity and classification as well as acoustic scene perception. 
\end{IEEEbiography}
